### 2021-03-12 input/proposal.tex
small changes

Fog infrastructures are distributed systems comprising heterogeneous
machines interconnected by communication links. We do not consider
byzantine processes.

@@

Algorithm~\ref{algo:add} shows the instructions that implement
eventually consistent partitioning when weights are scalar values.  At
any time, a process running this protocol can add a logical partition
to its distributed system.  Figure~\ref{fig:add} illustrates its
behavior on a system comprising 4 processes $a$, $b$, $c$, and
$d$. Two processes $a$ and $c$ concurrently create a partition by
S-broadcasting their respective \underline{a}dd message: $\alpha_a^0$
and $\alpha_c^0$. They initialize their own state with the lowest
possible bound $0$ (see Line~\ref{line:lowestbound}), and send a
message to each of their neighbors by accumulating the corresponding
edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, Process $b$ receives $\alpha_{c}^{1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. Process $b$ discards $\alpha_{b}^{1.5}$, for it does
not improve its partition distance. Processes $c$ and $d$ will never
hear of Process $a$'s partition.  In Figure~\ref{fig:addD}, processes
discard last transiting messages. The system converged to the optimal
partitioning.  Transitive relationships ensure that each process gets
its closest source while accumulation of weights ensures that messages
propagation terminates.

@@

In this section, we introduce \NAME, a wait-free reactive protocol for
logical partitioning in dynamic distributed systems the cost of which
actually depends on its usage: When the system becomes quiescent,
processes eventually converge to their respective partition and do not
require further communication afterward.

Each process is stateless, works autonomously and asynchronously, in a
peer-to-peer fashion. Each process broadcasts each change to its
neighborhood, for the state of its neighbors may depend on this change
as well. Yet, generated traffic remains \TODO{low} using scoped
broadcast. Messages that carry changes travel through the network
depending on partition of processes, stopping as soon as they
encounter uninterested processes. We demonstrate that \NAME guarantees
consistent partitioning despite different order in message deliveries
from one process to another.

This section starts by describing \NAME's functioning by detailing its
operation to avoid inconsistent states due to ordering and staleness
of delivered messages. This section ends with a complexity analysis of
proposed protocols.

@@

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system. All processes
that belong to this partition must eventually choose another partition
to belong to. Since the number of partitions does not monotonically
increase in the system any longer, each process requires a vector of
versions that monotonically increases over delivered operations.

@@

\TODO{Paths and \NAME synergize well, for paths tend to be smaller as the
number of sources increase in the system.}

>>>>

In this section, we introduce model and notations to provide a general
definition of scoped broadcast in distributed systems.  Distributed
systems such as Edge infrastructures comprise heterogeneous machines
interconnected by communication links. We do not consider byzantine
processes.

@@

Algorithm~\ref{algo:add} shows the instructions that implement
eventually consistent partitioning when weights are scalar values, and
processes only add new partitions to the system.  At any time, a
process running this protocol can add a logical partition to its
distributed system.  Figure~\ref{fig:add} illustrates its behavior on
a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition by S-broadcasting their
respective \underline{a}dd message: $\alpha_a^0$ and
$\alpha_c^0$. They initialize their own state with the lowest possible
bound $0$ (see Line~\ref{line:lowestbound}), and send a message to
each of their neighbors by accumulating the corresponding edge weight
(see Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process
$b$ receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition.  In Figure~\ref{fig:addD}, processes discard last
transiting messages. The system converged to the optimal partitioning.
Transitive relationships ensure that each process gets its closest
source while accumulation of weights ensures that messages propagation
terminates.

@@

In this section, we introduce \NAME, a wait-free reactive protocol for
dynamic logical partitioning in dynamic distributed systems the cost
of which actually depends on its usage. At any time, processes can add
\emph{and} remove partitions from the system. When the system becomes
quiescent, processes eventually converge to their respective partition
and do not require further communication afterward.

Each process is stateless, works autonomously and asynchronously, in a
peer-to-peer fashion. Each process broadcasts each change to its
neighborhood, for the state of its neighbors may depend on this change
as well. Yet, the traffic generated to to adapt the scope of
S-broadcast remains bounded, for it uses the principles of scoped
broadcast itself. Messages that carry changes travel through the
network depending on partition of processes, stopping as soon as they
encounter uninterested processes. We demonstrate that \NAME guarantees
consistent partitioning despite different order in message deliveries
from one process to another.

%% This section starts by describing \NAME's functioning by detailing its
%% operation to avoid inconsistent states due to ordering and staleness
%% of delivered messages. This section ends with a complexity analysis of
%% proposed protocols.

@@

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system. All processes
that belong to this partition must eventually choose another partition
to belong to.

\begin{definition}[Happens-before $\rightarrow$~\cite{lamport1978time}]
  The transitive, irreflexive, and antisymmetric happens-before
  relationship defines a strict partial order between events. Two
  messages are concurrent if none happens before the other.
\end{definition}

\begin{definition}[\TODO{Last win order}]
  For any $b_p(m) \rightarrow b_p(m')$, no process can deliver $m$ if
  it has delivered $m'$.
\end{definition}

\begin{definition}[\TODO{Adaptive scope}]
  Eventual consistent partitioning in presence of dynamic
  partitioning. Eventually get the last partition, eventually remove
  all outdated control information.
\end{definition}

Since the number of partitions does not monotonically increase in the
system any longer, each process requires a vector of versions that
monotonically increases over delivered operations.

@@

\TODO{Paths and \NAME synergies well, for paths tend to be smaller as the
number of sources increase in the system.}
